%!TEX root = ThesisLKN.tex
\pdfbookmark[1]{Abstract}{sec:abstract}  % Bookmark im pdf file
\chapter*{Abstract}
\label{sec:abstract}

With more and more robots deployed in human populated areas, it becomes very urgent to solve a lot of challenges existing in mobile robot applications. Human tracking is one of these challenges, which is essential for robots to successfully cooperate with humans and fulfill their tasks. Bayesian Occupancy Filter (BOF) is a Bayesian filtering method for object tracking on occupancy grids, which has been successfully used in automotive applications. In this thesis work, we extend the BOF with human motion model to deal with human tracking in indoor environments. For each cell on a gird map, the motion model is represented as a set of probability distributions on the exit direction, conditioned on the entering direction of the current cell. In this way, the motion model is able to capture both place dependency and spatial correlation between cells. A Convolutional Neural Network (CNN) is trained to extract motion model from a static map. By learning from simulated human trajectories, the network is able to generalize motion patterns on maps that never been seen before. We demonstrate our tracking method on both simulated and real human tracking datasets. The results show that our method outperforms its baseline method in both cases. Further applications of our method are also discussed, including predicting future occupancies and frequently occupied areas on a static map.

